\chapter{Introduction}

% Define problem
% What we started with and initial problem
% What we are ended up doing (briefly)
% Say outline of report

Graffiti is an act of vandalism, most commonly encountered in the form of defacing buildings and public surfaces with spray paint. Graffiti is often seen as unpleasant, evoking feelings of disarray and public unrest. The paint is also harmful to building surfaces. Removing graffiti is expensive, which is why preventative measures need to be preferred. Currently, preventative methods usually occur after the vandalism has taken place, such as organizing cleanups or adding more enforcement.

To our knowledge, no research has been done on what causes graffiti in the first place and how it could be prevented in the future. Most machine learning research on graffiti has focused on reactive measures. These include using drones to find and clean up graffiti \cite{uav}, \cite{drone}, or using the graffiti to then track down the perpetrators \cite{gang}.

Our research aims to understand the causes of graffiti on a more fundamental level to build a predictive model to prevent further graffiti. Features found in city layouts are analysed for potential correlations with graffiti, and are tested in different machine learning models to find best predictive accuracy. These predictions could then be potentially used, for example, to identify areas with high risks of graffiti or help with cleaning efforts. Additionally we will try to build an explainable model to illustrate what features in city layouts correlate with graffiti, with the goal of providing information for city planners to plan for graffiti-proof cities.

The following chapter discusses the methodology of how we collected, pre-processed and built models from that data. The next chapter shows the outcomes of our project, and what academic as well as applied knowledge we have obtained. We then conclude by summarizing our work and hinting towards any future work which may take place. The results and findings can be found on our \href{https://cowkeyman.github.io/PredictingGraffitiUsingCityLayouts/}{blog} in the \href{https://cowkeyman.github.io/PredictingGraffitiUsingCityLayouts/results.html}{results page}.
